ggalluvial: Layered Grammar for Alluvial Plots

### 2020-04-16 README.rmd
fix links in README per CRAN issues

This is a [**ggplot2** extension](http://www.ggplot2-exts.org/) for alluvial plots.

@@

```{r eval=TRUE}
titanic_wide <- data.frame(Titanic)
head(titanic_wide)
ggplot(data = titanic_wide,
       aes(axis1 = Class, axis2 = Sex, axis3 = Age,
           y = Freq)) +
  scale_x_discrete(limits = c("Class", "Sex", "Age"), expand = c(.1, .05)) +
  xlab("Demographic") +
  geom_alluvium(aes(fill = Survived)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  theme_minimal() +
  ggtitle("passengers on the maiden voyage of the Titanic",
          "stratified by demographics and survival")
```

@@

Contributions in any form are more than welcome! Pretty much every fix and feature of this package derives from a problem or question posed by someone with datasets or design goals i hadn't anticipated. See the [CONTRIBUTING](CONTRIBUTING.md) file for guidance, and please respect the [Code of Conduct](CODE_OF_CONDUCT.md).

>>>>

This is a [**ggplot2** extension](https://exts.ggplot2.tidyverse.org/) for alluvial plots.

@@

```{r eval=TRUE}
titanic_wide <- data.frame(Titanic)
head(titanic_wide)
ggplot(data = titanic_wide,
       aes(axis1 = Class, axis2 = Sex, axis3 = Age,
           y = Freq)) +
  scale_x_discrete(limits = c("Class", "Sex", "Age"), expand = c(.2, .05)) +
  xlab("Demographic") +
  geom_alluvium(aes(fill = Survived)) +
  geom_stratum() + geom_text(stat = "stratum", infer.label = TRUE) +
  theme_minimal() +
  ggtitle("passengers on the maiden voyage of the Titanic",
          "stratified by demographics and survival")
```

@@

Contributions in any form are more than welcome! Pretty much every fix and feature of this package derives from a problem or question posed by someone with datasets or design goals i hadn't anticipated. See the [CONTRIBUTING](https://github.com/corybrunson/ggalluvial/blob/master/CONTRIBUTING.md) file for guidance, and please respect the [Code of Conduct](https://github.com/corybrunson/ggalluvial/blob/master/CODE_OF_CONDUCT.md).
